Volunteers in the Clouds: an Architecture for Low Cost Massively Distributed Evolutionary Computation

### 2015-07-10 volunteer-clouds-ieee-ci-si.tex
Starting to write this

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

>>>>

% correct bad hyphenation here
\hyphenation{op-tical net-works}

@@

\author{Juan-J.~Merelo, %Add your name here
}% <-this % stops a space
\thanks{JJ Merelo is with the Dept. of Computer Architecture and Technology and CITIC University of Granada
e-mail: (jmerelo@ugr.es).}% <-this % stops a space
%Add the rest here

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Evolutionary algorithm, distributed computing, internet computing, social networks, 
\end{IEEEkeywords}
